---
title: "Data Types"
author: "R package build"
date: '2022-02-21'
slug: data-types
categories: []
tags: []
---

## Install Packages 
```{r}
library(tidyverse)
```

## Load Data
```{r}
url <- "https://raw.githubusercontent.com/spencergoldberg1/tidyverse/main/cat-lovers.csv"
cat_lovers <- read_csv(url)
view(cat_lovers)
```
## View Data
```{r}
cat_lovers %>%
  summarise(mean_cats = mean(number_of_cats))

?mean
```
## Why won't is still work?
```{r}
cat_lovers %>%
  summarise(mean_cats = mean(number_of_cats, na.rm = TRUE))
glimpse(cat_lovers)
```
## Fixing errors with numerical data
```{r}
cat_lovers %>%
  mutate(number_of_cats = case_when(
    name == "Ginger Clark" ~ 2,
    name == "Doug Bass"    ~ 3,
    TRUE                   ~ as.numeric(number_of_cats)
    )) %>%
  summarise(mean_cats = mean(number_of_cats))

```
```{r}
cat_lovers %>%
  mutate(
    number_of_cats = case_when(
      name == "Ginger Clark" ~ "2",
      name == "Doug Bass"    ~ "3",
      TRUE                   ~ number_of_cats
      ),
    number_of_cats = as.numeric(number_of_cats)
    ) %>%
  summarise(mean_cats = mean(number_of_cats))
```
## Coercing number of cats to be numeric data
```{r}
cat_lovers <- cat_lovers %>%
  mutate(
    number_of_cats = case_when(
      name == "Ginger Clark" ~ "2",
      name == "Doug Bass"    ~ "3",
      TRUE                   ~ number_of_cats
      ),
    number_of_cats = as.numeric(number_of_cats)
    )
glimpse(cat_lovers)
```
Data Types- Coercion
```{r}
typeof(TRUE)
typeof("hello")
typeof(1.335)
typeof(7L)
typeof(7)
typeof(1:3)
```
## Concatenation
```{r}
c(1, 2, 3)
c("Hello", "World!")
c(c("hi", "hello"), c("bye", "jello"))
```

## Converting between different data types
```{r}
x <- 1:3
x
```
```{r}
y <- as.character(x)
y
typeof(y)
```

```{r}
x <- c(TRUE, FALSE)
x
typeof(x)
```
```{r}
y <- as.numeric(x)
y
typeof(y)
```

## Converting between type without intention
```{r}
c(1, "Hello")
c(FALSE, 3L)
```
```{r}
c(1.2, 3L)
c(2L, "two")
```
## Explicit vs. implicit coercion
Explicit coercion is when you call a function like as.logical(), as.numeric(), as.integer(), as.double(), or as.character()

Implicit coercion happens when you use a vector in a specific context that expects a certain type of vector

## Special Values
```{r}
pi / 0
0 / 0
1/0 - 1/0
1/0 + 1/0
```
## NA's are special
```{r}
x <- c(1, 2, 3, 4, NA)
mean(x)
mean(x, na.rm = TRUE)
summary(x)
```
```{r}
typeof(NA)
```


