---
title: Importing Data
author: R package build
date: '2022-02-23'
slug: importing-data
categories: []
tags: []
---

# Reading rectangular data into R

### Installing Packages
```{r}
library(tidyverse)
```


## Reading Data
```{r}
url <- "https://raw.githubusercontent.com/spencergoldberg1/tidyverse/main/nobel.csv"
nobel <- read_csv(url)
nobel
```
## Writing Data
```{r}
df <- tribble(
  ~x, ~y,
  1,  "a",
  2,  "b",
  3,  "c"
)
write_csv(df, file = "df.csv")
```
## Reading from created file
```{r}
read_csv("df.csv")
```
## Variable names
```{r}
url <- "https://raw.githubusercontent.com/spencergoldberg1/tidyverse/main/edibnb-badnames.csv"
edibnb_badnames <- read_csv(url)
names(edibnb_badnames)
view(edibnb_badnames)
```

## Option 1 - Define column names
```{r}
edibnb_col_names <- read_csv(url,
                             col_names = c("id", "price", 
                                           "neighbourhood", "accommodates",
                                           "bathroom", "bedroom", 
                                           "bed", "review_scores_rating", 
                                           "n_reviews", "url"))
names(edibnb_col_names)
```
## Option 2 - Format text to snake_case
```{r}
edibnb_clean_names <- read_csv(url) %>%
  janitor::clean_names()
names(edibnb_clean_names)
```

## Variable Types
```{r}
url <- "https://raw.githubusercontent.com/spencergoldberg1/tidyverse/main/df-na.csv"
df_na <- read_csv(url)
```
## Option 1. Explicit NAs
```{r}
read_csv(url, 
         na = c("", "NA", ".", "9999", "Not applicable"))
```
## Option 2. Specify column types
```{r}
read_csv(url, col_types = list(col_double(), 
                                            col_character(), 
                                            col_character()))
```


# Case Stude
## Favorite Foods
```{r}
fav_food_url <- "https://raw.githubusercontent.com/spencergoldberg1/tidyverse/main/favourite-food.csv"
fav_food <- read_csv(url)
fav_food
```
## Variable Names
```{r}
fav_food <- read_csv(fav_food_url) %>%
  janitor::clean_names()
fav_food
```
## Handling NAs
```{r}
fav_food <- read_csv(fav_food_url,
                       na = c("N/A", "99999")) %>%
  janitor::clean_names()
fav_food
```
## Make age numeric
```{r}
fav_food <- fav_food %>%
  mutate(
    age = if_else(age == "five", "5", age),
    age = as.numeric(age)
    )
glimpse(fav_food)
```
## Socio-economic status
```{r}
fav_food %>%
  count(ses)
```
## Make ses factor
```{r}

fav_food <- fav_food %>%
  mutate(ses = fct_relevel(ses, "Low", "Middle", "High"))
fav_food %>%
  count(ses)
```
## Putting it all together
```{r}
fav_food <- read_csv(fav_food_url, na = c("N/A", "99999")) %>%
  janitor::clean_names() %>%
  mutate(
    age = if_else(age == "five", "5", age), 
    age = as.numeric(age),
    ses = fct_relevel(ses, "Low", "Middle", "High")
  )
fav_food
```
## Writing file then reading it back
```{r}
write_csv(fav_food, file = "fav-food-clean.csv")
fav_food_clean <- read_csv("fav-food-clean.csv")
fav_food_clean
```
## What happened to ces again?
```{r}
fav_food_clean %>%
  count(ses)
```


