---
title: "Data Classes"
author: "R package build"
date: '2022-02-23'
slug: data-classes
categories: []
tags: []
---

## Factors 
```{r}
x <- factor(c("BS", "MS", "PhD", "MS"))
x


typeof(x)
class(x)
```

## More on factors
```{r}
library(tidyverse)
glimpse(x)
as.integer(x)
```

## Dates
```{r}
y <- as.Date("2020-01-01")
y

typeof(y)
class(y)
```
## More on Dates
```{r}
as.integer(y)
as.integer(y) / 365 # roughly 50 yrs
```
## Data Frames
```{r}
df <- data.frame(x = 1:2, y = 3:4)
df

typeof(df)
class(df)
```

## Lists
```{r}
l <- list(
  x = 1:4,
  y = c("hi", "hello", "jello"),
  z = c(TRUE, FALSE)
)
l
```
## Lists and Data Frames
```{r}
df
df %>%
  pull(y)
```
## Read Data in as character strings
```{r}
url <- "https://raw.githubusercontent.com/spencergoldberg1/tidyverse/main/cat-lovers.csv"
cat_lovers <- read_csv(url)
glimpse(cat_lovers) %>%
  knitr::kable()
```
## Plotting cat_lovers
```{r}
ggplot(cat_lovers, aes(x = handedness)) + geom_bar()
```
## Use forcats to manipulate factors
```{r}
cat_lovers %>%
  mutate(handedness = fct_infreq(handedness)) %>%
  ggplot(mapping = aes(x = handedness)) +
  geom_bar()
```
## Hotels Graph
```{r}
library(tidyverse)
url <- "https://raw.githubusercontent.com/spencergoldberg1/tidyverse/main/hotels.csv"
hotels <- read_csv(url)
view(hotels)
```
## Line graph of hotels
```{r}
hotels %>%
  select(starts_with("arrival_"))

```
### Construct Dates
```{r}
library(glue)
hotels %>%
  mutate(
    arrival_date = glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}")
    ) %>% 
  relocate(arrival_date)
view(hotels)
```
### Count Bookings per date
```{r}
hotels %>%
  mutate(arrival_date = glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}")) %>%
  count(arrival_date)
```
### Visualise bookings per date
```{r}
hotels %>%
  mutate(arrival_date = glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}")) %>%
  count(arrival_date) %>%
  ggplot(aes(x = arrival_date, y = n, group = 1)) +
  geom_line()
```
### REVISED Construct dates "as dates"

```{r}
library(lubridate)
hotels %>%
  mutate(
    arrival_date = ymd(glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}"))
    ) %>% 
  relocate(arrival_date)
```
### Count bookings per date
```{r}
hotels %>%
  mutate(arrival_date = ymd(glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}"))) %>% 
  count(arrival_date)
```
### Visualise bookings per date
```{r}
hotels %>%
  mutate(arrival_date = ymd(glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}"))) %>% 
  count(arrival_date) %>%
  ggplot(aes(x = arrival_date, y = n, group = 1)) +
  geom_line()
```
### Visualise using a smooth curve
```{r}
hotels %>%
  mutate(arrival_date = ymd(glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}"))) %>% 
  count(arrival_date) %>%
  ggplot(aes(x = arrival_date, y = n, group = 1)) +
  geom_smooth()
```

