---
title: "Professor Evaluations"
author: "R package build"
date: '2022-02-28'
slug: professor-evaluations
categories: []
tags: []
---

# Preliminaries
## Importing Librairies
```{r}
library(moderndive)
library(tidyverse)
library(skimr)
library(gapminder)
```

## Importing Data
```{r}
evals_ch5 <- evals %>%
  select(ID, score, bty_avg, age)
```

## Explore the data
```{r}
glimpse(evals_ch5)
```

## Getting Samples from the data
```{r}
evals_ch5 %>%
  sample_n(size = 5)
```

## Mean and Median of BTY and Score
```{r}
evals_ch5 %>%
  summarize(mean_bty_avg = mean(bty_avg), mean_score = mean(score),
            median_bty_avg = median(bty_avg), median_score = median(score))
```
## Five Number Summary
```{r}
evals_ch5 %>% select(score, bty_avg) %>% skim()
```

## Scatter Plot of Score Vs. Bty_avg
```{r}
plot(evals_ch5$score, evals_ch5$bty_avg)
```
## Get the correlation between Score and Bty_avg
```{r}
evals_ch5 %>% 
  get_correlation(formula = score ~ bty_avg)

evals_ch5 %>% 
  summarize(correlation = cor(score, bty_avg))
```
## Data Visualization
```{r}
ggplot(evals_ch5, aes(x = bty_avg, y = score)) +
  geom_point() +
  labs(x = "Beauty Score", 
       y = "Teaching Score",
       title = "Scatterplot of relationship of teaching and beauty scores")
```
## Adding the line of best fit
```{r}
ggplot(evals_ch5, aes(x = bty_avg, y = score)) +
  geom_point() +
  labs(x = "Beauty Score", y = "Teaching Score",
       title = "Relationship between teaching and beauty scores") +  
  geom_smooth(method = "lm", se = FALSE)
```
## Looking at Linear Regression Table
```{r}
# Fit regression model:
score_model <- lm(score ~ bty_avg, data = evals_ch5)
# Get regression table:
get_regression_table(score_model)
```
## Using the get_regression_points() function
```{r}
regression_points <- get_regression_points(score_model)
regression_points
```
## Exploratory data analysis
```{r}
library(gapminder)
gapminder2007 <- gapminder %>%
  filter(year == 2007) %>%
  select(country, lifeExp, continent, gdpPercap)
glimpse(gapminder2007)
```

## Selecting samples from gapminder
```{r}
gapminder2007 %>% sample_n(size = 5)
```

## Using the skim function to explore gapminder
```{r}
gapminder2007 %>%
  select(lifeExp, continent) %>%
  skim()
```

## Plotting the data
```{r}
ggplot(gapminder2007, aes(x = lifeExp)) +
  geom_histogram(binwidth = 5, color = "white") +
  labs(x = "Life expectancy", y = "Number of countries",
       title = "Histogram of distribution of worldwide life expectancies")
```
```{r}
ggplot(gapminder2007, aes(x = lifeExp)) +
  geom_histogram(binwidth = 5, color = "white") +
  labs(x = "Life expectancy", 
       y = "Number of countries",
       title = "Histogram of distribution of worldwide life expectancies") +
  facet_wrap(~ continent, nrow = 2)
```
## Box plot of the data
```{r}
ggplot(gapminder2007, aes(x = continent, y = lifeExp)) +
  geom_boxplot() +
  labs(x = "Continent", y = "Life expectancy",
       title = "Life expectancy by continent")
```

## Computing the mean and median of the lifeExp
```{r}
lifeExp_by_continent <- gapminder2007 %>%
  group_by(continent) %>%
  summarize(median = median(lifeExp), 
            mean = mean(lifeExp))

glimpse(lifeExp_by_continent)
```

## Linear regression
```{r}
lifeExp_model <- lm(lifeExp ~ continent, data = gapminder2007)
get_regression_table(lifeExp_model)
```

```{r}
regression_points <- get_regression_points(lifeExp_model, ID = "country")
regression_points
```
## Fitting the regression model 
```{r}
# Fit regression model:
score_model <- lm(score ~ bty_avg, 
                  data = evals_ch5)

# Get regression points:
regression_points <- get_regression_points(score_model)
regression_points
```
## Computing the sum of squared residuals
```{r}
# Compute sum of squared residuals
regression_points %>%
  mutate(squared_residuals = residual^2) %>%
  summarize(sum_of_squared_residuals = sum(squared_residuals))
```
## Regression table of data
```{r}
# Fit regression model:
score_model <- lm(formula = score ~ bty_avg, data = evals_ch5)
# Get regression table:
get_regression_table(score_model)
```
## Cleaning the data using tidy() fromn the broom package
```{r}
library(broom)
library(janitor)
score_model %>%
  tidy(conf.int = TRUE) %>%
  mutate_if(is.numeric, round, digits = 3) %>%
  clean_names() %>%
  rename(lower_ci = conf_low, upper_ci = conf_high)
```

```{r}
library(broom)
library(janitor)
score_model %>%
  augment() %>%
  mutate_if(is.numeric, round, digits = 3) %>%
  clean_names() %>%
  select(-c("std_resid", "hat", "sigma", "cooksd", "std_resid"))
```

